\documentstyle{letter}

\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=9in  % text height can be bigger for a longer letter
\textwidth=5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}
\signature{Stavros Aronis}
\address{Mr. Stavros Aronis \\ Karaiskaki 3 \\ 16675, Glyfada, GR}

\begin{letter}{To Erlang Solutions}

\opening{Dear Sir/Madam,}

I'm writing this letter to express my interest in working in Erlang Solutions as
an intern during the summer of 2011. I've found the opening positions while
searching online for a summer internship, preferably one that could make use of
my experience in programming.

I have graduated in February from the National Technical University of Athens
with a degree in Electrical and Computer Engineering, presenting a thesis on
Dialyzer, the DIscrepancy AnaLYZer for ERlang programs, under the supervision of
Kostis Sagonas. In the year before my graduation I've been using Erlang as a
tool for academic research, while at the same time developing extensions that
improved the practical aspects of Dialyzer. I have been seeking ever since to
use the experience I gained in the development of real-world applications in
Erlang and the position you offer is ideal for this goal.

After my graduation in February, I've continued my collaboration with Kostis
Sagonas in both extending Dialyzer with new features and general support and bug
fixing. You can see my work in the various patches I've sent to the Erlang/OTP
repository in github.com. Beyond that, I've aided in the development of a
complete testing environment for Dialyzer that has been recently launched online
(Kostis presented it in Erlang Factory San Franscisco). The environment combines
Linux scripting with static site generation to present the results of running
Dialyzer on about 150 public Erlang applications. In the following months I plan
to put my Erlang and Dialyzer experience into good use and send patches to the
projects that have issues!

I am interested in working in Erlang Solutions between June 15th and August
15th. I would be excited to travel to any of the three locations offered. I will
promptly respond to any inquiries you may express via e-mail in
aronisstav@gmail.com or via phone in +306972232377.

\closing{Sincerely yours,}

\end{letter}
\end{document}
